Timeliness of security updates for Android

### 2014-08-15 securityupdates.tex
Vulnerability table comes from avo rather than da now
Compute bouncycastle latencies
Use a table to display version latency information

\input{dastats}
\input{avostats}
\newcommand{\percMarketShare}{XX\%~\cite{TODO}}
\newcommand{\daNumDevices}{\daNumOSDevices}
\newcommand{\daDeviceDays}{\daOSTotalDaysData}
% Num versions since \daStartDate
\newcommand{\bouncyCastleNumVersions}{A}
\input{countversions}
%\newcommand{\opensslNumVersions}{B}
\newcommand{\apacheLibsNumVersions}{C}
\newcommand{\apacheLibsNumLibs}{E}
%\newcommand{\linuxNumVersions}{D}

@@

\daTabAndVulns

@@

The number of updates shipped by upstream open source projects is calculated by scraping the releases pages for those projects.

>>>>

\input{dastats}
\input{avostats}
\newcommand{\percMarketShare}{XX\%~\cite{TODO}}
\newcommand{\daNumDevices}{\daNumOSDevices}
\newcommand{\daDeviceDays}{\daOSTotalDaysData}
% Num versions since \daStartDate
\input{countversions}
\newcommand{\apacheLibsNumVersions}{C}
\newcommand{\apacheLibsNumLibs}{E}

@@

\avoTabAndVulns

@@

The number of updates shipped by upstream open source projects is calculated by scraping the releases pages for those projects, from which we can also obtain the release dates.
By comparing the tags in the android git version repositories for upstream projects with Android version numbers and examining the version of the upstream project under that tag we computed which upstream project versions were included in each version of Android.
This allows us to compute the latency between an upstream project being released and it being included in Android, this is shown in Table~\ref{tab:update_ecosystem}.
\begin{table}
\centering
\begin{tabular}{l|r|r}
Project	&	\# releases	&	latency \\ \hline
linux	&	\linuxNumVersions	&	\linuxMeanUpdateLatency \\
openssl	&	\opensslNumVersions	&	\opensslMeanUpdateLatency \\
bouncycastle	&	\bouncycastleNumVersions	&	\bouncycastleMeanUpdateLatency \\
\end{tabular}
\caption{Flow of updates from upstream projects into Android. Number of updates as in Figure~\ref{fig:update_ecosystem}, latency in days for all pairs of versions we have data on.}
\label{tab:update_ecosystem}
\end{table}
